### 2016-02-01 p00-ch00-intro/intro.tex
Improve the intro architecture + objectives section

\section{Architecture}
\label{sec:intro:arch:crit}

In this section, we present a high-level overview of design goals that we pursue in this research. 
%Equivalently, the effectiveness and success of this research is measured upon the achievement of the discussed goals and objectives.

@@

\paragraph{Scalability} 
Asynchronous message passing in ABS is a fit for distributed systems.
In such systems, the number of messsages delivered among actors in the 
environment is not predictable at runtime.
Therefore, distribution challenges performance efficiency or scalability.
The goal is to ensure the actor system scales in performance with least 
influence from the number of asynchronous messages delivered in the system.
\TODO{Discuss with Frank and drop this.}

\paragraph{Modularity} 
One of the main goals of this research is to create a modular and reusable
software artifact. 
This can be achieved only by producing an API for ABS semantics that is
indepedent from any specific ABS backend.
\TODO{Elaborate on why an API library is modular for ABS}
The scope of the research spans to a number of layers revolving around ABS
 language:
\begin{itemize}
\item \emph{Compiling ABS to a target programming language}
One first objective is to compile an ABS model to a target programming language.
% The compilation can be at \emph{source-to-source} or \emph{source-to-bytecode} level.
In addition, to be able to integrate generated code from ABS into other legacy systems, it is crucial that generated code is readable and of acceptable quality.\TODO{Use software engineering terms here}
Target languages potentially include mainstream programming languages such as
Java, Erlang, Haskell, and Scala.
Thus, the ABS programmer should be able to use an ABS compiler to compile
their ABS models to the target languages.
\TODO{Why not the previous ABS Java backend suffered from software engineering}
\item \emph{Using ABS concurrency as an API in an existing programming language}
The ABS language is precisely expressed with structural operational semantics~\cite{johnsen2012abs} in addition to its syntax definition.
The semantics of ABS can be delivered in a programming language
as Application Programming Interface (API) as long as the programming language provides sufficient constructs to respect ABS language semantics.
In addition, such ABS programming API should be \emph{verifiable}.
If an ABS mapping to a programming API is provided, a programmer is able to
take advantage of ABS semantics without directly programming in ABS.
Such capability from ABS enables industry users of mainstream languages to
model their systems in ABS semantics using their programming languages and
platforms.
\item \emph{Modelling in ABS}
ABS language provides a rigorous semantics to model concurrent
and distributed systems.
For practical reasons, the user (that can be a programmer, an analysist, or a researcher) 
desires to have access to a tool-set and IDE that allows working with ABS 
models in a user-friendly way.
The ABS IDE and tool-set developers should be able to easily reuse and compose
over existing modules and components.
\end{itemize}

% Based on the scopes and layers of usage of this research, we aim to provide 
% a highly modular architecture in design and implementation.
% The goal is verifiable based on produced artifacts of this research in terms
% of their \emph{usability}, \emph{re-usability}, and \emph{composability} in
% different contexts.

\paragraph{Extensibility}
It is a common practice in software engineering that components are developed with a mixture of \emph{configuration}, \emph{extension} and \emph{composition}.
Hence, delivering the ABS language features as an API brings about a new requirement: to configure or extend the API. 
In particular, the ABS programmer should be able to extend the API to customized requirements. \TODO{Expand?}
%The extensibility is provided either through configuration of the API or API extension.

\Behrooz{It's worth to include the figure but needs more work to justify its presence and how it relates to this thesis.}
Figure~\ref{fig:arch} presents the general architecture of the implementation.

\TODO{Relate the criteria in this section on how they lead to a natural modular architecture in the figure.}

\begin{figure}[h]
\centering
\includegraphics[scale=0.3]{../figs/Arch.eps}
\caption[General Architecture]{General Architecture of ABS API and Java Language Backend}
\label{fig:arch}
\end{figure}

>>>>

\section{Objectives and Architecture}
\label{sec:intro:arch:crit}

In this section, we present a high-level overview of design goals that we pursue in this research.

@@

\paragraph{Scalability} 
Asynchronous message passing in ABS is a fit for distributed systems.
In such systems, the number of messsages delivered among actors in the 
environment is not predictable at runtime.
The goal is to ensure the actor system scales in performance with least 
influence from the number of asynchronous messages delivered in the system.

\begin{figure}[t]
\centering
\includegraphics[scale=0.3]{../figs/Arch.eps}
\caption[General Architecture]{General Architecture of ABS API and Java Language Backend}
\label{fig:arch}
\end{figure}

\paragraph{Modularity} 
We approach ABS modelling and development with a component-based or modular 
software engineering practices.
The scope of the research spans to a number of layers around ABS language:

\begin{itemize}
\item \emph{Compiling ABS to a target programming language}
One first objective is to compile an ABS model to a target programming language.
Target languages potentially include mainstream programming languages such as
Java, Erlang, Haskell, and Scala.
Thus, the ABS programmer should be able to use an ABS compiler to compile
their ABS models to the target languages.
We propose a new architecture for ABS tool-set and engineering that enables
different programming language utilize the same architecture.
\item \emph{Using ABS concurrency as an API in an existing programming language}
The ABS language is precisely expressed with structural operational semantics~\cite{johnsen2012abs} in addition to its syntax definition.
The semantics of ABS can be delivered in a programming language
as Application Programming Interface (API) as long as the programming language provides sufficient constructs to respect ABS language semantics.
In addition, such ABS programming API should be \emph{verifiable}.
If an ABS mapping to a programming API is provided, a programmer is able to
take advantage of ABS semantics without directly programming in ABS.
Such capability from ABS enables industry users of mainstream languages to
model their systems in ABS semantics using their programming languages and
platforms.
\item \emph{Modelling in ABS}
ABS language provides a rigorous semantics to model concurrent
and distributed systems.
For practical reasons, the user (that can be a programmer, an analysist, or a researcher) 
desires to have access to a tool-set and IDE that allows working with ABS 
models in a user-friendly way.
The ABS IDE and tool-set developers should be able to easily reuse and compose
over existing modules and components.
\end{itemize}

This approach yields to a modular architecture presented in 
Figure~\ref{fig:arch}.

% \paragraph{Extensibility}
% It is a common practice in software engineering that components are developed with a mixture of \emph{configuration}, \emph{extension} and \emph{composition}.
% Hence, delivering the ABS language features as an API brings about a new requirement: to configure or extend the API. 
% In particular, the ABS programmer should be able to extend the API to customized requirements. \TODO{Expand?}
